\documentclass[11pt]{article}
\input{../calcnotes.sty}
\fancyhead[R]{1.2 Functions and Graphs}

\begin{document}

\noindent The values of one variable often depend on another. We call this a function. We define a function as a rule that assigns a \underline{\hspace{2cm}} element of the range ($R$) to each element in the domain ($D$). Counter-examples:

\vspace{1.5cm}

\noindent Since the purpose of mathematics is to model the world, a function is pretty important. We write a function as:

\vspace{1.5cm}

\noindent What is the function that expresses the area of a circle?

\vspace{1.5cm}

\noindent Domain is the \underline{\hspace{2cm}}. Range is the \underline{\hspace{2cm}}. What are the domain and range for the circle function?

\vspace{1.5cm}

\noindent What is interval notation? Show $-3 < x \le 6$ with interval notation (and any other way you can think of). What about for the circle above?

\noindent Identify the domain and range of the following graphs. Use interval notation.

\vspace{0.5cm}

\begin{align*}
    y=\frac{1}{x} && y=\sqrt{x}
\end{align*}

\vspace{0.5cm}

\begin{align*}
    y=\sqrt{4-x^2} && y=x^\frac{2}{3}
\end{align*}

\newpage

\noindent What is the definition of an even function? An odd function?

\vspace{1.5cm}

\noindent How do we know if a function is even or odd by looking at its graph?

\vspace{1.5cm}

\noindent Determine if the following functions are odd, even, or neither.

\begin{align*}
    f(x) = x^2 && f(x) = x^2 + 1 && f(x) = x && f(x) = x + 1
\end{align*}

\vspace{1.5cm}

\noindent How do we graph a piecewise function? Graph and find the domain and range:

\vspace{0.5cm}

\noindent
\begin{minipage}[c]{0.5\textwidth}
\[f(x) =
\begin{cases}
    -x, & x < 0 \\
    x^2, & 0 \le x \le 1 \\
    1, & x > 1
\end{cases}
\]

\vspace{1cm}
\noindent Domain: \underline{\hspace{4cm}}

\vspace{0.8cm}
\noindent Range: \underline{\hspace{4cm}}
\end{minipage}
\begin{minipage}[c]{0.5\textwidth}
\centering
\begin{tikzpicture}
    \begin{axis}[
        axis lines = middle,
        xlabel = $x$,
        ylabel = $y$,
        xmin = -3, xmax = 3,
        ymin = -1, ymax = 4,
        xtick={-2,-1,1,2},
        ytick={1,2,3},
        grid = both,
        grid style={line width=.1pt, draw=gray!10},
        major grid style={line width=.2pt,draw=gray!50},
        width=6cm,
        height=6cm,
        tick label style={font=\tiny}
    ]
    \end{axis}
\end{tikzpicture}
\end{minipage}

\newpage

\noindent Graph the following: $f(x) = |x - 2| + 3$. Then write it as a piecewise function. Also find the domain and range.

\vspace{0.5cm}

\noindent
\begin{minipage}[t]{0.5\textwidth}
    \centering
    \begin{tikzpicture}
        \begin{axis}[
            axis lines = middle,
            xlabel = $x$,
            ylabel = $y$,
            xmin = -1, xmax = 6,
            ymin = -1, ymax = 7,
            xtick={-1,0,1,2,3,4,5},
            ytick={1,2,3,4,5,6},
            grid = both,
            grid style={line width=.1pt, draw=gray!10},
            major grid style={line width=.2pt,draw=gray!50},
            width=6.5cm,
            height=6.5cm,
            tick label style={font=\tiny}
        ]
        \end{axis}
    \end{tikzpicture}
\end{minipage}

\vspace{1cm}

\noindent Finally, what is a composite function? If $f(x) = x - 7$ and $g(x) = x^2$, what is $f(g(x))$? What is $(f \circ g)(x)$? What is $g(f(2))$?

\vspace{1.5cm}

\noindent Composite functions are used a lot in Calculus.

\vspace{1.5cm}

\end{document}
